\section{Introduction}
Physics beyond the Standard Model could manifest itself by observing highly collimated multiple leptons that result from the decay of a highly boosted resonance. Detail study of the reconstruction efficiency of collimated muons in the CMS detector will demonstrate the feasibility of such a search with the startup data. In addition, similar to track jet reconstruction, lepton jets will be reconstructed with any optimal selection of leptons track quality.
The lepton jet algorithm chosen shows excellent angular resolutions and unambiguous association to a single primary vertex in the interaction region, making Lepton Jets transparent to pile-up effects.
The proton-proton collisions, delivered by the Large Hadron Collider (LHC) at CERN at a center-of-mass energy  of 7 TeV, and recorded by the CMS detector in 2010 provided us with a sample of XXX Jpsi decaying to collimated muons to test out lepton jet algorithm performance.
In section 2 reconstruction of collimated muons is studied using Monte Carlo Gun samples In section 3 we demonstrate the performance of a simple lepton jet algorithm and compare it to the results of section 2. In addition we lepton jet tagging efficiency for various boosts and orientation of the decay resonance for lepton jets composed of two or four muons. In section 4 we show few identification criteria that can be used to suppress the background.
and in the last section we use demonstrate the performance of the lepton jet algorithm using a Jpsi control sample from the data.



